Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-20 awipev-CO2.Rmd
More on figures Eliminate outliers visually Eliminate pH spectro when profiler was at more than 1 depth in the same hour Only use pH spectro data when profiler was below 6 m

mytheme <- theme_bw() +
  theme(axis.text.x=element_text(size=16, color="black"),
        axis.title.x=element_text(face="bold", size=16),
        axis.text.y=element_text(size=16, color="black"),
        axis.title.y=element_text(face="bold", size=16),
        plot.title = element_text(face="bold", size=14)
)

@@

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
#d_all <
```

@@

```{r Combine discrete and continous data, echo=FALSE}

# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m). New column "sal_mix" is created.

- 1 SBE45 inside the Ferrybox (sal_fb)
- 5 CTD > 8 meters depth (sal_insitu_ctd)

@@

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox
sal_xts <- dplyr::select(d_all, datetime, sal_fb)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc",
    label = "pco2_calc",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
```

@@

# add spectro points that are not taking into consideration
d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_mix,
      NA
    )
  )

@@

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

>>>>

@@

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  )
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(month = month(month(datetime))) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE))
#restore datetime and date which are mangled by the murtates above
d_all$datetime <- d_hour$datetime
d_all$date <- d_hour$date
```

@@

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_mix = ifelse(n_depth_ctd == 4, ph_s_sf_temp_mix, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_mix = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_mix, NA)) # only use ph spectro data when profiler was below 6 m

discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m). New column "sal_mix" is created and is the one used in ESSD paper.

- 1 SBE45 inside the Ferrybox (sal_fb)
- 5 CTD > 8 m depth (sal_insitu_ctd)

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_mix < 34 ~ NA_real_,
      TRUE ~ sal_mix
    )
  )
```

@@

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc",
    label = "pco2_calc",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    pco2_corr = case_when(
      date > as.Date("2016-04-01") &
        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2017-08-01") &
        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
      TRUE ~ pco2_corr
    )
  )
```

@@

# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
# shown as white triangles on the plot
d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_mix,
      NA
    )
  )

@@

# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    ph_dur_corr = case_when(
          ph_dur_corr < 8 ~ NA_real_,
      date > as.Date("2018-05-18") &
        date <  as.Date("2018-05-19") & ph_dur_corr < 8.16 ~ NA_real_,
      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2017-09-25") &
        date <  as.Date("2017-10-01") & ph_dur_corr < 8.07 ~ NA_real_,
      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
      TRUE ~ ph_dur_corr
    )
  )

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# prepare data and remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))

pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

## Figures for ESSD paper

```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face="bold", size=size_labs, margin=margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face="bold", size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
        aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 1.5, b = 0, l = 1.5, unit = "lines")
  )
}
# select time series data
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = "In situ temperature (°C)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_temp.png")
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = "Salinity") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_sal.png")
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = expression(paste("C", O[2], " partial pressure (", mu, "atm)"))) +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_pco2.png")
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>% 
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  labs(title = "", x = "Time", y = expression(paste("p", H[T]))) +
  scale_color_manual(values=c("blue", "red"), 
                       name="",
                       breaks=c("pHint_tot_sf", "ph_dur_corr"),
                       labels=c("SeaFET", "Durafet")) +
  Mytheme(size_labs = 8)
print(ts_ph)

ggsave(filename = "figures/ts_ph.png")
